Total Platform Cyber Protection

### 2016-08-21 paper.tex
added tags for ccs concepts, used ccs code generator, might need more codes custom modded the numbers to 400, to emphasize that all are same level of importance default is 500, 300, 100

% Title portion
\title{Total Platform Cyber Protection}
\author{GANG ZHOU
\affil{College of William and Mary}
YAFENG WU
\affil{University of Virginia}
TING YAN
\affil{Eaton Innovation Center}
TIAN HE
\affil{University of Minnesota}
CHENGDU HUANG
\affil{Google}
JOHN A. STANKOVIC
\affil{University of Virginia}
TAREK F. ABDELZAHER
\affil{University of Illinois at Urbana-Champaign}}
% NOTE! Affiliations placed here should be for the institution where the
%       BULK of the research was done. If the author has gone to a new
%       institution, before publication, the (above) affiliation should NOT be changed.
%       The authors 'current' address may be given in the "Author's addresses:" block (below).
%       So for example, Mr. Abdelzaher, the bulk of the research was done at UIUC, and he is
%       currently affiliated with NASA.

\begin{abstract}
Multifrequency media access control has been well understood in
general wireless ad hoc networks, while in wireless sensor networks,
researchers still focus on single frequency solutions. In wireless
sensor networks, each device is typically equipped with a single
radio transceiver and applications adopt much smaller packet sizes
compared to those in general wireless ad hoc networks. Hence, the
multifrequency MAC protocols proposed for general wireless ad hoc
networks are not suitable for wireless sensor network applications,
which we further demonstrate through our simulation experiments. In
this article, we propose MMSN, which takes advantage of
multifrequency availability while, at the same time, takes into
consideration the restrictions of wireless sensor networks. Through
extensive experiments, MMSN exhibits the prominent ability to utilize
parallel transmissions among neighboring nodes. When multiple physical
frequencies are available, it also achieves increased energy
efficiency, demonstrating the ability to work against radio
interference and the tolerance to a wide range of measured time
synchronization errors.
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>  
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}

%
% End generated code
%

@@

\keywords{Wireless sensor networks, media access control,
multi-channel, radio interference, time synchronization}

>>>>

% Title portion
\title{Total Platform Cyber Protection}

%TODO Adam: Not sure if anon submission so just leaving like this for now
\author{
%First Author
%\affil{Arizona State University}
%Second Author
%\affil{Arizona State University}
%Third Author
%\affil{Arizona State University}
%Fourth Author
%\affil{Arizona State University}
%Fifth Author
%\affil{Arizona State University}
%Sixth Author
%\affil{Arizona State University}
%Seventh Author
%\affil{Arizona State University}
}
% NOTE! Affiliations placed here should be for the institution where the
%       BULK of the research was done. If the author has gone to a new
%       institution, before publication, the (above) affiliation should NOT be changed.
%       The authors 'current' address may be given in the "Author's addresses:" block (below).
%       So for example, Mr. Abdelzaher, the bulk of the research was done at UIUC, and he is
%       currently affiliated with NASA.

% TODO Sai: Discuss story with yeganeh and get a nice little abstract here
\begin{abstract}
Multifrequency media access control has been well understood in
general wireless ad hoc networks, while in wireless sensor networks,
researchers still focus on single frequency solutions. In wireless
sensor networks, each device is typically equipped with a single
radio transceiver and applications adopt much smaller packet sizes
compared to those in general wireless ad hoc networks. Hence, the
multifrequency MAC protocols proposed for general wireless ad hoc
networks are not suitable for wireless sensor network applications,
which we further demonstrate through our simulation experiments. In
this article, we propose MMSN, which takes advantage of
multifrequency availability while, at the same time, takes into
consideration the restrictions of wireless sensor networks. Through
extensive experiments, MMSN exhibits the prominent ability to utilize
parallel transmissions among neighboring nodes. When multiple physical
frequencies are available, it also achieves increased energy
efficiency, demonstrating the ability to work against radio
interference and the tolerance to a wide range of measured time
synchronization errors.
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
\begin{CCSXML}
	<ccs2012>
	<concept>
	<concept_id>10002978.10003001.10010777</concept_id>
	<concept_desc>Security and privacy~Hardware attacks and countermeasures</concept_desc>
	<concept_significance>400</concept_significance>
	</concept>
	<concept>
	<concept_id>10002978.10003001.10003003</concept_id>
	<concept_desc>Security and privacy~Embedded systems security</concept_desc>
	<concept_significance>400</concept_significance>
	</concept>
	<concept>
	<concept_id>10002978.10003006.10003007</concept_id>
	<concept_desc>Security and privacy~Operating systems security</concept_desc>
	<concept_significance>400</concept_significance>
	</concept>
	<concept>
	<concept_id>10002978.10003022</concept_id>
	<concept_desc>Security and privacy~Software and application security</concept_desc>
	<concept_significance>400</concept_significance>
	</concept>
	</ccs2012>
\end{CCSXML}

\ccsdesc[400]{Security and privacy~Hardware attacks and countermeasures}
\ccsdesc[400]{Security and privacy~Embedded systems security}
\ccsdesc[400]{Security and privacy~Operating systems security}
\ccsdesc[400]{Security and privacy~Software and application security}
%
% End generated code
%

@@

%TODO Sai: Add keywords here
\keywords{}
